Validation of Visual Statistical Inference, with Application to Linear Models

### 2012-04-11 paper_jasa.tex
defined visual test p-value

%If $N$ individuals evaluate a lineup plot independently, the number of successful evaluations, $U \sim \text{Binom} (N,\frac{1}{m})$ and we report a  $p$-value of at most $Pr(U \ge u)= \sum_{k \ge u}^N {{N \choose k} (\frac{1}{m})^k(1-\frac 1m)^{(N-k)}}$ where $u$ is the observed number of successful evaluations. %Notice that when $N=1$, this $p$-value is $\frac1m$.

@@

% HH: I think this is covered by making power a property of the test
% In general,  $Pr(\text{Reject } H_0)$ is determined by the type of test being conducted.

>>>>

 %Notice that when $N=1$, this $p$-value is $\frac1m$.

@@

When $K$ individuals evaluate a lineup plot independently, the number of successful evaluations, $U \sim \text{Binom} (K,1/m)$  under $H_0$. Thus we define $p$-value for visual test $T_{\theta}$ as in definition \ref{dfn:pval}.
\begin{dfn} \label{dfn:pval}
The $p$-value of A visual test $T_{\theta}$ is at most $Pr(U \ge u)= \sum_{k \ge u}^K {{K \choose k} (\frac{1}{m})^k(1-\frac 1m)^{(K-k)}}$ where $u$ is the observed number of successful evaluations.
\end{dfn}
% HH: I think this is covered by making power a property of the test
% In general,  $Pr(\text{Reject } H_0)$ is determined by the type of test being conducted.
